Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-04-22 paper/paper.tex
Partial work on evaluation and such.

@@

\usepackage[font=footnotesize]{subcaption}

@@

\begin{document}
	\title{Revisiting~the~Classics: Online~RL~in~the~Programmable~Data-Plane}

@@

\section{Introduction}

@@

This paper contributes:
\begin{itemize}
	\item A thing (?? REFERENCE SECTION). Here's how that thing is utterly fantastic and will change the world, or not.
\end{itemize}

@@

@@

@@

@@

?? relate update/execute operations here? i.e., policy execute needs only ALU add, train needs add+mul+shr. or in RL section? Should that come first?

@@

\subsection{Action and Update Computation}
\approachshort{} applies the insights of \textcite{DBLP:journals/firai/TravnikMSP18} to minimise action latency; an action is computed, sent out into the environment, and only then is the underlying policy updated.
Using one of the below strategies chosen at compile time, a state vector is tile coded, converted into action probabilities, and an action is chosen according to current choice of $\epsilon$ (exploration parameter).
This is then written out to the environment as in \cref{sec:agent-environment-communication}.
If updates are enabled, \approachshort{} then checks an internal hashmap for a previous state-action pair matching the current instruction source, and if found then a policy update is performed.
Updates are computed using \emph{single-step semi-gradient Sarsa}, though modification to support other single-step methods would be trivial.
The new state- or tiles-action pair is then written into storage

@@

In the NFP architecture we use, physical cores (MEs) each have 8 hardware threads (contexts): all contexts on an ME share the same program and employ zero-cost context switches on I/O.
Each core then provides 8 worker threads, though in the parallel case one must be dedicated to monitoring work acknowledgements.
Two main firmware models govern how the computation-intensive parts of these tasks (tile-coding, action preference list construction, policy updates) are carried out:
\begin{description}
	\item[Single (\cref{fig:single-and-parallel:single})] Separate threads listen for new states, and each performs its work sequentially. Computing an action list requires a \emph{read lock} on the policy. If an update occurs, the core requests a \emph{write lock} before updating, greatly limiting online throughput. Tile lists are stored for update computation.
	\item[Parallel (\cref{fig:single-and-parallel:parallel})] Threads cooperate on processing state vectors, minimising latency. Workers have a fixed list of work items, while a master thread sends compute/update commands before awaiting worker completion. Work items are disjoint, requiring no policy locks. State vectors are stored for update computation.
\end{description}
Each offers a different point of optimisation; if updates are disabled, then the \emph{single} model can maximise throughput, while the \emph{parallel} model is designed to minimise decision latency and needs no locks for updating the policy (increasing online learning throughput).

@@

\subsection{Reconfiguration}
?? Compile-time config of bit-depth, what else?

\begin{itemize}
	\item (Re)-configurable at runtime.
	\item Custom DSCP marker acts as indicator of RL packets (i.e., bother with parsing past UDP). This trick is copied from \textcite{DBLP:conf/isca/LiLYCSH19}.
	\item P4 parser extracts headers, parser state and payload passed over ring to another core dedicated to RL operations.
	\item Policy dimensions, size, action count, tiling strategies, learning parameters ($\alpha, \gamma, \epsilon$, related falloffs) can all be chosen and changed live.
\end{itemize}

?? Reconfig triggers cacheing of per-work item data: tiling locations, ....

Written in rust.

\subsection{Work Allocation}
?? WHy

?? How

?? Work index correlates with complexity (and can be estimated a-priori).

\subsection{Policy Storage}
?? Why

?? Trained online or installed by block copy from control/data planes.

?? Blocks of dense quantised tiles: each an action preference list.

?? Tiling data is split into regions of memory based on access time: higher-dimension tilings are sent to further NUMA regions (EMEM/IMEM).

\subsection{Variable Quantisation Bitdepth}
Compile time eh

?? Mention that BB SIMD failed here.

??

?? Batching of reads. ?? action value batching  (relate to bitdepth).

?? Lower bitdepth can mean more actions, more tilings, more dimensions in tilings, higher perf.

\subsection{Notes from chat with others}
This approach can be used to generate transferable policies/samples for other models.

Potential: low-latency train for some specific points, and high throughput for others? Think on the exact note I took...

``can have accel'd offline, train online subset w/ my approach''

THis might mean "do 32-bit online", then downsample to 8-bit policy for high-throughput mode.

Can changes in trained policy be used to transfer to a more complex function approximator elsewhere?

\subsection{Limitations}
Known/understood (but not implemented)?
\begin{itemize}
	\item Figure out PIF rule installation.
	\begin{itemize}
		\item Not doable through P4 na\"{i}vely. Handing back rules to controller is expensive: need another action to deliberately use its own hash table etc., then batch back as faster P4 rules.
	\end{itemize}
\end{itemize}

\subsection{Targeting other device classes}
While this design caters primarily to Netronome's SmartNIC devices, many aspects of this design have clear analogues in NICs of similar form-factor, such as their close NetFPGA SUME cousins.
For instance, the availability of other cores can be handled by designing additional off-path functional units, much like the floating-point adders used by \textcite{DBLP:conf/isca/LiLYCSH19}.
Rather than general-purpose cross-core communication, an RL functional unit would be hard-wired to and from the custom actions that interface with it, using the P4$\rightarrow$NetFPGA toolchain to offer the base framework and granular control over packet and flow selection.
Further optimisations arise from this model: a NetFPGA design would be able to replicate and optimise further on this concept of dedicated, low-latency communication between functional units.
Consider a single, shared, read-only register between RL functional ...
?? think about really really carefully lest Reviewer 2 murder you
?? Parallel, atomic writes at the required resolution.
?? No bit stuffing required.

@@

\section{Potential Integrations}

\subsection{DDoS Defence}
?? Link to my own work
?? Explain how every part may be substituted
?? Bump-in-the-wire at edge nodes.

@@

\subsection{Something host-specific?}
Accelerate something at an end-host...

\section{Evaluation}

\subsection{Experimental Setup}
Evaluation of \approachshort{} was performed on server blades hosting a single Netronome Agilio LX 1x100GbE SmartNIC (NFP-6480, \SI{1.2}{\giga\hertz}).
These ran Ubuntu 18.04.5 LTS (4.15.0-140-generic x86\_64) on Intel Xeon Bronze 3204 CPUs (\SI{1.9}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
Control programs were built using rustc 1.51.0.
All timing and throughput measurements were repeated over 5000 trials.

@@

\section{Results}

@@

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/work-strat-32bit}
	}
	\caption{?? Choice of work strategy is pretty important I guess}
\end{figure}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-work}
	}
	\caption{?? More work means More time. ?? Max Parallelisation. ?? Bitdepth affects independent cores more.}
\end{figure}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-core}
	}
	\caption{?? More cores means less time ?? Max-size work (129 work-items). ?? Need to dedicate 3 worker to beat independent cores. ?? Sharper perf increase when new physical core added. ?? up to 31 due to master thread.}
\end{figure}

How do we evaluate this without looking into classification performance?
\begin{itemize}
	\item Analytically?
	\begin{enumerate}
		\item Prove that tile splitting scheme over memory hierarchy can improve performance.
		\begin{itemize}
			\item Hit rate of different tiles according to tile dimensionality?
			\item Access time for each tier of memory hierarchy.
		\end{itemize}
	\end{enumerate}
	\item Experimentally?
	\begin{enumerate}
		\item Create ``VNF'' testbed: mirror traffic from switch to a host for telemetry processing/flow state. Send flow state over to another node who computes RL actions. RL actions installed on switch.
		\begin{itemize}
			\item Why not co-host RL computation with telemetry? Could be separate functions, could want to ensure that neither impacts the performance of the other.
		\end{itemize}
		\item Create ``PDP'' testbed: Load firmware, pass in traffic. Traffic processing/action compute/table mod occurs in PDP.
		\item What traffic? Healthy mix of attack (UDP), Discord legit Opus VoIP traffic, HTTP bulk-transfer traffic.
		\item Measure $t_{1 \cdots 3}$ according to \cref{fig:state-slip} in both VNF and PDP contexts.
		\begin{description}
			\item[$t_1$]
			\begin{description}
				\item[PDP] Packet ingress $\rightarrow$ INT Island $\rightarrow$ State arrival in Control ME.
				\item[VNF] Packet mirror time $\rightarrow$ telemetry VNF $\rightarrow$ state arrival in agent vnf.
			\end{description}

@@

\begin{acks}
	This work was supported in part by the \grantsponsor{gs-epsrc}{Engineering and Physical Sciences Research Council}{https://epsrc.ukri.org/} [grant~\grantnum{gs-epsrc}{EP/N509668/1}].
\end{acks}

>>>>

\usepackage[title]{appendix}

@@

\usepackage[font=footnotesize]{subcaption}
\usepackage{awesomebox}

@@

\newcounter{insightc}
\newenvironment{insight}
	{
		\begin{tipblock}\refstepcounter{insightc}\textbf{Insight \theinsightc:}\em
	}
	{
		\end{tipblock}
	}

\begin{document}
	\title{Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane}

@@

\setlength{\aweboxleftmargin}{0.12\linewidth}
\setlength{\aweboxcontentwidth}{1.97\linewidth}

\section{Introduction}
?? REDO ME

@@

This paper contributes:
\begin{itemize}
	\item An analysis of why in-NIC RL is best-placed to interact with the network, and how classical RL methods and quantisation ensure computational feasibility (\cref{sec:motivation}),
	\item \emph{\approachshort{}}: a general-purpose in-NIC RL agent which scales with allocated device resources to meet latency or throughput demands (\cref{sec:design}),
	\item Potential integrations of \approachshort{} with state-of-the-art PDP applications to perform fully in-NIC, automated DDoS mitigation and ?? OTHER THING (\cref{sec:potential-integrations}),
	\item In-depth evaluation of how our approach affects carried dataplane traffic, performs under different policy sizes, and improves upon explicit offloading to produce a \SI{0}{$\times$} latency reduction (\crefrange{sec:evaluation}{sec:results}). ??actual val
\end{itemize}

@@

\begin{insight}
	Classical RL methods are computationally simple to update online, and inference and learning are embarrassingly parallel.
\end{insight}

@@

\begin{insight}
	Online control problems benefit from low-latency, local execution and training (i.e., in-NIC/switch).
\end{insight}

@@

\begin{insight}
	Low-port density programmable network devices often have spare resources and extra capabilities beyond the PISA specification which can aid asynchronous, local compute.
\end{insight}

@@

?? relate update/execute operations here? i.e., policy execute needs only ALU add (and whatever is needed for tile code), train needs add+mul+shr. or in RL section? Should that come first?

@@

\subsection{Action and Update Computation}
\approachshort{} applies the insights of \textcite{DBLP:journals/firai/TravnikMSP18} to minimise action latency; an action is computed, sent out into the environment, and only then is the underlying policy updated.
Using one of the below strategies chosen at compile time, a state vector is tile coded, converted into action probabilities, and an action is chosen according to current choice of $\epsilon$ (exploration parameter).
This is then written out to the environment as in \cref{sec:agent-environment-communication}.
If updates are enabled, \approachshort{} then checks an internal hashmap for a previous state-action pair matching the current instruction source, and if found then a policy update is performed.
Updates are computed using \emph{single-step semi-gradient Sarsa}, though modification to support other single-step methods would be trivial.
The new state- or tiles-action pair is then written into storage.

@@

In the NFP architecture we use, physical cores (MEs) each have 8 hardware threads (contexts): all contexts on an ME share the same program and employ zero-cost context switches on I/O.
Each core then provides 8 worker threads, though in the parallel case one must be dedicated to monitoring work acknowledgements.
Two main firmware models govern how the computation-intensive parts of these tasks (tile-coding, action preference list construction, policy updates) are carried out:
\begin{description}
	\item[Single (\cref{fig:single-and-parallel:single})] Separate threads listen for new states, and each performs its work sequentially. Computing an action list requires a \emph{read lock} on the policy. If an update occurs, the core requests a \emph{write lock} before updating, greatly limiting online throughput. Tile lists are stored for update computation.
	\item[Parallel (\cref{fig:single-and-parallel:parallel})] Threads cooperate on processing state vectors, minimising latency. Workers have a fixed list of work items, while a master thread sends compute/update commands before awaiting worker completion. Work items are disjoint, requiring no policy locks. State vectors are stored for update computation.
\end{description}
Each offers a different point of optimisation; if updates are disabled, then the \emph{single} model can maximise throughput, while the \emph{parallel} model is designed to minimise decision latency and needs no locks for updating the policy (increasing \emph{online learning} throughput).

@@

\subsection{Reconfigurability}
\approachshort{} allows for policy dimensions, size, action count, tiling strategies, and algorithmic learning parameters ($\alpha, \gamma, \epsilon$, related falloffs) to be chosen and changed at runtime.
This extends to policy data, which may be imported from an offline pre-trained model via such packets, and exported via the NFP binary support package on the host machine.
Some aspects must be chosen at compile time; bit-depth, work allocation strategy, and maximum policy/tiling/state sizes---these govern core operation or allocated memory regions.

In our implementation, configuration packets are carried over UDP and signalled to the P4 parser using a reserved DSCP value as used by \textcite{DBLP:conf/isca/LiLYCSH19}.
While we primarily use this to automate parser generation, this also allows for configuration packets to be received from only trusted hosts over the dataplane if needed via P4 rules.
Our control packet generation library (and evaluation frameworks which build upon it) are written in Rust.

\subsection{Work Allocation}
Due to the lack of dynamic memory allocation and to simplify action-value lookups, policies cannot be effectively stored sparsely.
As a consequence, tiling space requirements scale exponentially with dimension count, and so higher-dimension tilings must be placed in memory regions large enough to allocate space for them.
As a result, tilings are split across memory regions, giving different access and compute costs to different tasks---ranging over CLS, CTM and EMEM in increasing latency.

We use a simple first-fit work placement algorithm run on the NFP, placing the largest work item into the least loaded thread of the least loaded core.
The cost of any individual work item (according to its dimension count and memory location) was estimated offlin.
This work allocation and any cached per-work-item values are recomputed when any configuration is installed or changed.

\subsection{Variable Quantisation Bit Depth}
At compile-time, \approachshort{} can be configured to use \SIlist[list-final-separator = { \translate{or} }]{32;16;8}{\bit} values in input states and its internal policies.
Naturally, smaller bit depths reduce the storage required for policies, tiling data, and stored state-action pairs---allowing more complex problems to be modelled using more dimensions or fine-grained policies.
Through the lens of computational efficiency, reduced bit depth allows action preference lists to be read using fewer I/O operations (as more values may fit into a single machine word).
We had investigated bit-stuffing several such values into a single word for our atomic writeback mechanism (as the platform offers both \SIlist{32;64
}{\bit} atomic addition).
This is analogous to SIMD---through clever use of padding bits---but we found that manipulating tiles into the correct format added \SI{10}{\percent} extra overhead.

\subsection{Notes from chat with Rhys}
?? Where/how to fit this in? I think it's a useful point.

The two compute models discussed here need not be homogeneously deployed.
For instance, in a networked deployment a subset of \approachshort{} nodes could be \SI{32}{\bit} \emph{parallel} agents, training online, while most other nodes ran \SI{8}{\bit} \emph{single} designs to meet throughput guarantees.
The control plane would then be responsible for combining, downsampling, and distributing these improved policies between remaining agents.
This can be taken further still, using policy deltas or execution traces to enable out-of-path transfer learning for more complex function approximators such as neural networks.

%Potential: low-latency train for some specific points, and high throughput for others? Think on the exact note I took...
%
%``can have accel'd offline, train online subset w/ my approach''
%
%THis might mean "do 32-bit online", then downsample to 8-bit policy for high-throughput mode.
%
%Can changes in trained policy be used to transfer to a more complex function approximator elsewhere?

\subsection{Limitations}
Unfortunately, direct rule installation into P4 tables from the SmartNIC itself is not, in general, possible.
To achieve line-rate match-action table lookup, platforms like NFP use accelerated datastructures (e.g., DCFL~\parencite{DBLP:conf/infocom/TaylorT05}) which must be computed by the controller over the \emph{entire rule set}.
Even through externs,

We instead suggest on NFP chips that externs or datapath stages which apply actions to packet processing should maintain a small local store of state-action pairs, and periodically send these back to the controller for batch rule installation.
This ensures that the vast majority of installed rules enjoy accelerated performance, while preventing rule installation delay on the newest decisions.
Platforms such as Intel Tofino greatly simplify this, with Tofino Native Architecture intrinsics such as \emph{Action Profiles/Selects} allowing a P4 action to be chosen based on a register value (i.e., an RL action).

\subsection{Targeting other device classes}
While this design caters primarily to Netronome's SmartNIC devices, many aspects of this design have clear analogues in NICs of similar form-factor, such as their close NetFPGA SUME cousins.
For instance, the availability of other cores can be handled by designing additional off-path functional units, much like the floating-point adders used by \textcite{DBLP:conf/isca/LiLYCSH19}.
Rather than general-purpose cross-core communication, an RL functional unit would be hard-wired to and from the custom actions that interface with it, using the P4$\rightarrow$NetFPGA toolchain to offer the base framework and granular control over packet and flow selection.
Further optimisations arise from this model: a NetFPGA design would be able to replicate and optimise further on this concept of dedicated, low-latency communication between functional units.
Consider a single, shared, read-only register between RL functional ...
?? think about really really carefully lest Reviewer 2 murder you
?? Parallel, atomic writes at the required resolution.
?? No bit stuffing required for SIMD-alike?.
?? More chances for vectorisation? Is that where we're falling down atm with 32-bit being weirdly optimal?

@@

\section{Potential Integrations}\label{sec:potential-integrations}
To show the general applicability and use of \approachshort{}, we propose two ideal integrations which would benefit most from in-NIC reinforcement learning; online DDoS attack mitigation (\cref{sec:integ-1}), and ?? OTHER THING (\cref{sec:integ-2}).
We support these using other state-of-the-art P4/PDP developments.

\subsection{DDoS Defence}\label{sec:integ-1}
?? Link to my own work
?? Explain how every part may be substituted

?? Bump-in-the-wire at edge nodes.

?? How does increased attack flow ratio affect the RL core? How does changing its params to increase its own throughput?
?? Remember the timed-random-selection; use the state coalescing trick indep discovered by you and those other guys.

?? Can the P4 dataplane be used to reduce/increase the number of flows used as inputs? (YES)

@@

\subsection{Something host-specific?}\label{sec:integ-2}
Accelerate something at an end-host... Flow control? Something datacentre-y? A novel CCA? What?

\section{Evaluation}\label{sec:evaluation}
We outline our performance evaluation of...

?? find something meaningful to put here.

\subsection{Experimental Setup}
Evaluation of \approachshort{} was performed on server blades hosting a single Netronome Agilio LX 1x100GbE SmartNIC (NFP-6480, \SI{1.2}{\giga\hertz}).
These ran Ubuntu 18.04.5 LTS (4.15.0-140-generic x86\_64) on Intel Xeon Bronze 3204 CPUs (\SI{1.9}{\giga\hertz}) and \SI{32}{\gibi\byte} RAM.
Control programs were built using rustc 1.51.0.
We run \approachshort{} on an island with \num{4} MEs of the NFP-6480 for a total of \num{32} hardware threads.
This is the maximum number of MEs on a single island which is not in use by an existing P4 pipeline.
Where feasible, we test \SIlist{32;16;8}{\bit} quantised arithmetic firmware versions.
All timing and throughput measurements were repeated over \num{5000} trials.

Policy sizes are set to those matching a real-world DDoS control application~\parencite{DBLP:journals/tnsm/SimpsonRP20}: 20-dimension state vectors, a bias tile and 16 full tiling sets (7$\times$1-dim, 8$\times$2-dim, 1$\times$4-dim), 8 tilings per dimension set, 6 tiles per dimension, choosing between 10 actions.

@@

\subsection{Experiments}

\fakepara{Raw inference and learning performance}
We compare how long it takes for \approachshort{} to compute actions and update its policy per state vector received, and report on the observed throughput of our designs.
We compare these against floating point and quantised implementations running on a commodity host machine.
This allows us to demonstrate the performance differences between the \emph{Single} and \emph{Parallel} configurations, particularly in how \emph{Single's} required policy locks impact throughput.
We also report on the derived throughput measures accounting for the locking behaviour of each.

Building on this, we vary the amount of allocated worker threads to show how \approachshort{} can scale to fit available compute resources on a device.
This also demonstrates the number of cores needed to achieve a given latency bound on a policy of representative complexity.
Moreover, to demonstrate how these costs vary as policy complexity increases, we vary the number of total dimensions included in the tiling.

?? NOT GOT OTHERS TO COMPARE AGAINST YET, JUST SELF.
?? Mention versus DNN latency in passing here?

\fakepara{Work allocation}
%?? Also our simple, ahead-of-time, work scheduler.
We verify that our heuristic, runtime work scheduler (\emph{Balanced}) makes meaningful use of the explicit memory hierarchy and cost of each work item.
We compare it versus several baselines: a \emph{Na\"{i}ve} chunked scheduler, a \emph{Random} baseline allocation, and a simple \emph{Modular} allocator (where a worker $j$ out of $w$ takes $k$ items given by $\mathit{work}_j=\left\{\left(j + i \times w\right) \bmod n_{\mathit{items}} \mid i \in [0,k) \right\}$).

\fakepara{End-to-end RL latency}
We compare the key RL decision-making latencies we discuss in \cref{fig:state-slip} ($t_1,t_2,t_3$) across 3 scenarios: completely in-NIC (\approachshort{}), offloading RL decisions to a SmartNIC's controller machine, and offloading to the controller of an OpenFlow-compatible switch (OvS).

?? NOT DONE YET
?? MOSTLY A PAPER EXERCISE FROM SOME OTHER MEASURES

\fakepara{Co-existence with the dataplane}
We measure maximum packet rate and bandwidth throughput of a P4 pipeline on our SmartNICs, both with and without \approachshort{}.
This allows us to quantify whether on-chip (out-of-path) execution impacts ordinary dataplane behaviour through indirect means: e.g., EMEM cache evictions or hidden resource contention.
In particular, we stress test both decisions and policy updates of our \emph{Parallel} design at full throughput.

?? NOT DONE YET.

\fakepara{Resource requirements}
Using the maximum policy size defined above, we investigate how the memory requirements imposed by \approachshort{} vary with the number of dedicated MEs, over and above a base P4 forwarding plane.

?? Not done yet: read these out from the IDE.

\fakepara{The impact of bit depth}
We further investigate how bit depth affects the accuracy of policy by varying the number of bits used to represent the mantissa of action values and input state.

\subsection{Results and Discussion}\label{sec:results}

@@

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-work}
	}
	\caption{?? More work means More time. ?? Max Parallelisation. ?? Bitdepth affects independent cores more. ?? latency version in appendix: \Cref{fig:vary-work-latency}}
\end{figure}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-core}
	}
	\caption{?? More cores means less time ?? Max-size work (129 work-items). ?? Need to dedicate 3 worker to beat independent cores. ?? Sharper perf increase when new physical core added. ?? up to 31 due to master thread. ?? latency version in appendix: \Cref{fig:vary-core-latency}}
\end{figure}

\fakepara{Raw inference and learning performance}
TEST

\fakepara{Work allocation}
?? \Cref{fig:work-alloc-32}

\begin{figure}
	\resizebox{1.0\linewidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/work-strat-32bit}
	}
	\caption{?? Choice of work strategy is pretty important I guess\label{fig:work-alloc-32}}
\end{figure}

\fakepara{End-to-end RL latency}
TEST

\fakepara{Co-existence with the dataplane}
TEST

\fakepara{Resource requirements}
?? \Cref{tab:resources}

\begin{table}
\caption{NFP memory use due to \approachshort{}. CLS and CTM are shared between all programs on the same island (placing our RL agent on i5), while EMEM and IMEM are shared between all NFP programs on a NIC.\label{tab:resources}}
\resizebox{\linewidth}{!}{
\begin{tabular}{@{}cSSSSSSSSSS@{}}
	\toprule Firmware & \multicolumn{2}{c}{EMEM} & \multicolumn{2}{c}{EMEM Cache} & \multicolumn{2}{c}{IMEM} & \multicolumn{2}{c}{i5.CLS} & \multicolumn{2}{c}{i5.CTM}\\
	& \multicolumn{1}{c}{\si{\mebi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} \\
	\midrule Base P4 & 6794.73 & 88.47 & 0 & 0 & 858.28 & 10.48 & 0 & 0 & 0 & 0 \\
	Single (1-core) & 6778.83 & 88.27 & 1737.91 & 18.86 & 1263.28 & 15.42 & 28.69 & 44.82 & 90 & 35.16 \\
	Single (4-core) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	Parallel (1-core) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	Parallel (4-core) & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
	\bottomrule
\end{tabular}
}
\end{table}

\fakepara{The impact of bit depth}
?? \Cref{fig:quant-acc}

\begin{acks}
	The authors would like to thank Rhys Simpson for his comments and discussions on SIMD-like optimisations.
	This work was supported in part by the \grantsponsor{gs-epsrc}{Engineering and Physical Sciences Research Council}{https://epsrc.ukri.org/} [grant~\grantnum{gs-epsrc}{EP/N509668/1}].
\end{acks}

\begin{appendices}
	\section{Old ``What could we do``?}
	How do we evaluate this without looking into classification performance?
	\begin{itemize}
		\item Analytically?
		\begin{enumerate}
			\item Prove that tile splitting scheme over memory hierarchy can improve performance.
			\begin{itemize}
				\item Hit rate of different tiles according to tile dimensionality?
				\item Access time for each tier of memory hierarchy.
			\end{itemize}
		\end{enumerate}
		\item Experimentally?
		\begin{enumerate}
			\item Create ``VNF'' testbed: mirror traffic from switch to a host for telemetry processing/flow state. Send flow state over to another node who computes RL actions. RL actions installed on switch.
			\begin{itemize}
				\item Why not co-host RL computation with telemetry? Could be separate functions, could want to ensure that neither impacts the performance of the other.
			\end{itemize}
			\item Create ``PDP'' testbed: Load firmware, pass in traffic. Traffic processing/action compute/table mod occurs in PDP.
			\item What traffic? Healthy mix of attack (UDP), Discord legit Opus VoIP traffic, HTTP bulk-transfer traffic.
			\item Measure $t_{1 \cdots 3}$ according to \cref{fig:state-slip} in both VNF and PDP contexts.
			\begin{description}
				\item[$t_1$]
				\begin{description}
					\item[PDP] Packet ingress $\rightarrow$ INT Island $\rightarrow$ State arrival in Control ME.
					\item[VNF] Packet mirror time $\rightarrow$ telemetry VNF $\rightarrow$ state arrival in agent vnf.
				\end{description}

@@

	\begin{figure}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/rl-perf-tester/vary-work-latency}
		}
		\caption{Latency! varying work.\label{fig:vary-work-latency}}
	\end{figure}

	\begin{figure}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/rl-perf-tester/vary-core-latency}
		}
		\caption{Latency! varying core count\label{fig:vary-core-latency}}
	\end{figure}
\end{appendices}
